\documentclass[12pt,a4paper]{article}
\usepackage[hidelinks]{hyperref}
\usepackage[hyperref=true,backend=bibtex,citestyle=ieee]{biblatex}
\usepackage[margin=1in]{geometry}
\usepackage[section]{placeins}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{appendix}
\usepackage{authblk}
\usepackage{caption}
\usepackage{csquotes}
\usepackage{enumerate}
\usepackage{enumitem}
\usepackage{float}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{indentfirst}
\usepackage{multirow}
\usepackage{subcaption}
\usepackage{svg}

\title{Message Authentication Code}
\author[1]{Chang Liu}
\author[1]{Liyan Jiang}
\author[1]{Yiwen Yang}
\affil[1]{Group 4, VE475, UM-JI}
\date{\today}
%Totally, you should upload your folder including only .tex and .bib to github
%Add your biblatex reference here
\addbibresource{introduction/ref.bib}
\addbibresource{implementation/ref.bib}
\addbibresource{application/ref.bib}
\addbibresource{security/new.bib}

\begin{document}
\begin{titlepage}
	\maketitle
	\begin{abstract}
		%here should be
		%\input{.../abstract.tex}
		Message Authentication Code (MAC), is a short piece of information used for authenticating a message \cite{crypto-net}. This project aims at performing some personal study on MAC as well as discussing the topic using cryptography analysis methods covered in the course, so as to acquire more knowledge in the cryptography field. We first briefly introduce the structure and process of MAC, then two implementations of MAC algorithm are explained in detail: Hash-based Message Authentication Code (HMAC) and Block Cipher-based Message Authentication Code (CMAC). Next, the security of both implementations is analyzed and attack methods are discussed. Finally we present the application of MAC in Transport Layer Security (TLS) Protocol.
	\end{abstract}
\end{titlepage}
\tableofcontents
\newpage
%Add your paragraphs here using \input
\input{introduction/introduction.tex}
\input{implementation/implementation.tex}
\input{security/main.tex}
\input{application/application.tex}

\section{Conclusion}

	In this project, we studied the mechanism and structure of MAC. We learnt that MAC plays a critical role in the authentication field, and it is widely used in Internet connection protocols. The general process of MAC is clearly explained, and we explored two implementations of MAC algorithms: HMAC and CMAC. The security of CMAC based on Poly1305-AES is proved to be as secure as AES, while HMAC is figured out to perform as a pseudorandom function. Beyond this, brute force and side channel attacks are also introduced. Through this work, we are able to further expand our knowledge in the vast cryptography area and improve major researching skills.

\newpage
\printbibliography
\end{document}